\section{Backend}
\subsection{Technologies and libraries}
\subsubsection{NodeJs}
Node.js is an open-source, cross-platform, back-end JavaScript runtime environment that runs on the
V8 engine and executes JavaScript code outside a web browser. Node.js lets developers use JavaScript
to write command line tools and for server-side scripting—running scripts server-side to produce
dynamic web page content before the page is sent to the user’s web browser. Consequently, Node.js
represents a "JavaScript everywhere" paradigm, unifying web-application development around a single
programming language, rather than different languages for server-side and client-side scripts.
\begin{itemize}
    \item \textbf{Used Version:}
\end{itemize}
\subsubsection{Serverless Framework}
The Serverless Framework is a free and open-source web framework written using Node.js. Serverless is the first
framework developed for building applications on AWS Lambda, a serverless computing platform provided
by Amazon as a part of Amazon Web Services.
\begin{itemize}
    \item \textbf{Used Version:}
\end{itemize}
\subsubsection{TypeScript}
TypeScript is a programming language developed and maintained by Microsoft. It is a strict syntactical
superset of JavaScript and adds optional static typing to the language. TypeScript is designed for the
development of large applications and transcompiles to JavaScript. As TypeScript is a superset of JavaScript,
existing JavaScript programs are also valid TypeScript programs.
\begin{itemize}
    \item \textbf{Used Version:}
\end{itemize}
\subsubsection{Amazon DynamoDB}
Amazon DynamoDB is a fully managed, multi-region, multi-active, durable, proprietary NoSQL database service that supports key-value
and document data structures and is offered by Amazon.com as part of the Amazon Web Services
portfolio.
\subsubsection{JSON}
JSON (JavaScript Object Notation) is an open standard file format, and data interchange format, that
uses human-readable text to store and transmit data objects consisting of attribute–value pairs and
array data types (or any other serializable value).
JSON is a language-independent data format. It was derived from JavaScript,
but many modern programming languages include code to generate and parse JSON-format data.
\subsubsection{Npm}
npm is the default package manager for the JavaScript runtime environment Node.js.
It consists of a command line client, also called npm, and an online database of public and paid-for private packages,
called the npm registry. The registry is accessed via the client, and the available packages can be browsed and
searched via the npm website.
\subsubsection{Yarn}
Yarn is a new package manager that replaces the existing workflow for the npm client or other package managers while
remaining compatible with the npm registry. It has the same feature set as existing workflows while operating faster,
more securely, and more reliably.
\subsection{Architecture}
\subsubsection{Main components}
\subsubsection{External services}
\subsubsubsection{Amazon API Gateway}
Amazon API Gateway is a fully managed service that makes it easy for developers to create, publish, maintain, monitor,
and secure APIs at any scale. APIs act as the "front door" for applications to access data, business logic,
or functionality from your backend services. Using API Gateway, you can create RESTful APIs and WebSocket APIs that
enable real-time two-way communication applications. API Gateway supports containerized and serverless workloads,
as well as web applications.
\subsubsubsection{Amazon Cognito}
Amazon Cognito lets you add user sign-up, sign-in, and access control to your web and mobile apps quickly and easily.
Amazon Cognito scales to millions of users and supports sign-in with social identity providers, such as Apple,
Facebook, Google, and Amazon, and enterprise identity providers via SAML 2.0 and OpenID Connect.
\subsubsubsection{AWS Lambda}
AWS Lambda is an event-driven, serverless computing platform provided by Amazon as a part of Amazon Web Services.
It is a computing service that runs code in response to events and automatically manages the computing resources required by that code.
\subsubsubsection{Amazon S3}
Amazon Simple Storage Service (Amazon S3) is an object storage service that offers industry-leading scalability,
data availability, security, and performance.
\subsubsubsection{Stripe}
Stripe is a service that allows developers to integrate secure payment processing into their websites and applications.
\subsection{Class diagrams}
\subsection{Sequence diagrams}