\section{Common technologies and libraries}
\subsection{utilities-techsweave}
Utilities-techsweave is an npm package created and published by Techsweave containing all functions, classes, interfaces and objects common to all microservices. It also contains an encapsulation of the calls to the api of the various microservices.
\begin{itemize}
  \item \textbf{Used Version: Latest}
  \item \textbf{Link: \url{https://www.npmjs.com/package/utilities-techsweave}}
  \item \textbf{Link: \url{https://github.com/techsweave/utilities}}
\end{itemize}
\subsection{Typescript}
TypeScript is a programming language developed and maintained by Microsoft. It is a strict syntactical
superset of JavaScript and adds optional static typing to the language. TypeScript is designed for the
development of large applications and transcompiles to JavaScript. As TypeScript is a superset of JavaScript,
existing JavaScript programs are also valid TypeScript programs.
\begin{itemize}
  \item \textbf{Used Version: 4.3.4}
  \item \textbf{Link: \url{https://aws.amazon.com/sqs/?nc1=h_ls}}
\end{itemize}
\subsection{JSON}
JSON (JavaScript Object Notation) is an open standard file format, and data interchange format, that
uses human-readable text to store and transmit data objects consisting of attribute–value pairs and
array data types (or any other serializable value).
JSON is a language-independent data format. It was derived from JavaScript,
but many modern programming languages include code to generate and parse JSON-format data.
\begin{itemize}
  \item \textbf{Link: \url{https://www.json.org/json-en.html}}
\end{itemize}
\subsection{npm}
npm is the default package manager\textsubscript{\textbf{G}} for the JavaScript runtime environment Node.js.
It consists of a command line client, also called npm, and an online database of public and paid-for private packages,
called the npm registry. The registry is accessed via the client, and the available packages can be browsed and
searched via the npm website.
\begin{itemize}
  \item \textbf{Used Version: 6.14.13}
  \item \textbf{Link: \url{https://www.npmjs.com/}}
\end{itemize}
% \subsection{yarn}
% Yarn is a new package manager that replaces the existing workflow for the npm client or other package managers while
% remaining compatible with the npm registry.
% \begin{itemize}
%   \item \textbf{Used Version: 1.22.10}
%   \item \textbf{Link: \url{https://yarnpkg.com/}}
% \end{itemize}
\subsection{ESLint}
ESLint is a tool for identifying and reporting on patterns found in ECMAScript/JavaScript code, with the goal of making code more consistent and avoiding bugs.
\begin{itemize}
  \item \textbf{Used Version: 7.26.0}
  \item \textbf{Link: \url{https://eslint.org/}}
\end{itemize}
\subsection{Stripe}
Stripe is a service that allows developers to integrate secure payment processing into their websites and applications.
\begin{itemize}
  \item \textbf{Used Version: 8.157.0}
  \item \textbf{Link: \url{https://stripe.com/en-it}}
\end{itemize}
\subsection{Amazon DynamoDB Expressions}
This library provides a number of abstractions designed to make dealing with Amazon DynamoDB expressions easier and more natural for JavaScript developers.
\begin{itemize}
  \item \textbf{Used Version: 0.7.3}
  \item \textbf{Link: \url{https://www.npmjs.com/package/@aws/dynamodb-expressions}}
\end{itemize}
